\cvsection{Courses, Pet projects}

\cvproject{Machine Learning}{MIPT course, Lector: K.V. Vorontsov}{\href{https://github.com/Panterrich/MachineLearning}{Github}}
Learned the basics of machine learning in regards to applying them to my future researches.
\medskip

\cvproject{Development on GoLang}{MIPT course}{\href{https://github.com/Panterrich/Gitfame}{Github}}
The course is based on \href{https://shad.yandex.ru}{Yandex School of Data Analysis}. Gitfame is the main project for the course.
\medskip

\cvproject{Concurrency}{MIPT course, Lector: Roman Lipovsky}{}
The course introduces a new viewpoint on asynchronous programming.
It covers synchronization primitives, schedulers, functional futures, fibers and coroutines.
\medskip

\cvproject{SSH}{}{\href{https://github.com/Panterrich/MySSH}{Github}}
Own implementation of SSH. Supports symmetric and asymmetric encryption, multi-user connection, file copying, Reliable UDP protocol implementation.
\medskip

\cvproject{JCC}{}{\href{https://github.com/Panterrich/JCC}{Github}}
AOT compiler written for JPL. JPL is its own turing-complete programming language.
Its main feature is that you can code a program in it both in hiragana and romaji (Latin).

\divider

\cvsection{Techical Skills}
\cvskill{Programming languages}
C, C++, Go, asm x86-64, Python
\medskip

\cvskill{Technologies}
Linux API, Boost, MPI, OpenMP
\medskip

\cvskill{Languages}
English - intermediate
\medskip

\cvskill{Other}
Networks, machine learning, computational maths

\divider

\cvsection{Interests}
\begin{itemize}
    \item Powerlifting
    \item Photography, student photo studio.
\end{itemize}

\divider

% \end{itemize}
